Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-17 paper-2023-acsos-pulverization.tex
begin a pass on section 4A

In this section,
we exercise the proposed framework with two case studies.
%
In the former,
we show a small-scale demonstrator of a safety system warning people when a room capacity is exceeded
to showcase the integration of the framework with established technologies\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-crowd-room}
};
in the latter,
we simulate a city-scale distributed application deployed for a urban event
and show how the dynamic reconfiguration may help achieving balance between energy consumption and \ac{qos}\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-evaluation}
}.
%
Both experiments have been released with a permissive open-source license and have been archived for future reference on Zenodo~\cite{TBD}.

@@

In this section we present a simple scenario where the pulverization framework is used to implement a crowd alert system:
we simulate a laboratory where a safety system warns people when they are too close to each other.
%
Each person is equipped with a wearable device that is able to detect the distance from other devices and send the distances data to the
alert system.
%
The people in the laboratory must observe a safety distance, and the system warns them when the distance is not respected by showing a red light
when they are too close to each other, and a green color when the distance is respected (see~\Cref{fig:crowd-alert}).
%
\begin{figure*}[ht]
    \centering
    \includegraphics[width=.8\textwidth]{figures/crow-laboratory-demo.drawio.pdf}
    \caption{
        Representation of the scenario described in the~\Cref{sec:small-scale-crowd-alert}
        where more the people are far from each other, more the color of the screen is green.
        More the people are close to each other, more the color of the screen is red.
        The blue dot represents the wearable device and the link between the devices represents the distance between them.
        The rectangle represents the monitor in the laboratory which shows the congestion level of the laboratory (via the color described above).
    }
    \label{fig:crowd-alert}
\end{figure*}
%
The system is composed of two kind of devices: \emph{wearable} and \emph{laboratory}.
%
The former represents the wearable devices that is worn by the people, and consists of the following pulverized components:
$\beta$, $\chi$, and $\sigma$.
%
The \emph{behaviour} ($\beta$) component is responsible for converting the raw data from the sensor into the distance
between the device and the others; the \emph{sensors} ($\sigma$) component is responsible for perceiving the other devices and
the \emph{communication} ($\chi$) component is responsible for sending the data to the alert system.
%
The latter represents the alert system and consists of the following pulverized components:
$\beta$, $\kappa$, $\chi$, and $\alpha$.
%
The \emph{behaviour} ($\beta$) component is responsible for evaluating the meand distance between the devices,
the \emph{actuators} ($\alpha$) is responsible for triggering the alarm showing a color in the screen,
and the \emph{communication} ($\chi$) component is responsible for receiving the data from the wearable devices.

>>>>

In this section,
we exercise the proposed framework through two case studies.
%
In the former,
we show a small-scale demonstrator of a safety system warning people when a room capacity is exceeded
to showcase the integration of the framework with established technologies\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-crowd-room}
};
in the latter,
we simulate a city-scale distributed application deployed for a urban event
and show how the dynamic reconfiguration may help achieving balance between energy consumption and \ac{qos}\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-evaluation}
}.
%
Both experiments have been released with a permissive open-source license and have been archived for future reference on Zenodo~\cite{TBD}.

@@

In this example, we exercise the framework on a real-world testbed
located in a laboratory.
%
In particular,
we want to avoid situations in which too many people are too close to each other in the same room for safety reasons.
%
To do so,
we equip each person with a wearable device that is able to detect the distance from other simialr devices via Bluetooth.
%
For the sake of simplicity,
in the experiment we relied on smartphones to emulate wearables,
and we used \meta{
    NICOLAS please write here (within meta, so that it remains blue)
    what you used to measure the signal strenght and estimate the distance.
    Even formulas, calibration procedures, and stuff
}
%
In our case the warning was issued through a monitor,
whose color was set to tones ranging from green to red depending on the average distance among people:
the shorter the distance, the more red the tone.
%
\Cref{fig:crowd-alert} shows a representation of the scenario.
%
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/crow-laboratory-demo.drawio.pdf}
    \caption{
        Representation of the scenario described in \Cref{sec:small-scale-crowd-alert}.
        graph dots represent wearables,
        and arcs lenghts represent the distance between them.
        %
        The rectangle at the bottom represents the monitor.
        %
        The closer the wearables are, the higher is the alert level
        (reddish tones).
        %
        \meta{NICOLAS riduci lo spazio vuoto fra i tre casi, così da guadagnare spazio. La legenda potrebbe essere messa sotto o sopra per guadagnarne di ulteriore}
    }
    \label{fig:crowd-alert}
\end{figure}
%
The system is composed of two kind of devices: \emph{wearable} and \emph{laboratory}.
%
The former represents the wearable devices that is worn by the people, and consists of the following pulverized components:
$\beta$, $\chi$, and $\sigma$.
%
The \emph{behaviour} ($\beta$) component is responsible for converting the raw data from the sensor into the distance
between the device and the others; the \emph{sensors} ($\sigma$) component is responsible for perceiving the other devices and
the \emph{communication} ($\chi$) component is responsible for sending the data to the alert system.
%
The latter represents the alert system and consists of the following pulverized components:
$\beta$, $\kappa$, $\chi$, and $\alpha$.
%
The \emph{behaviour} ($\beta$) component is responsible for evaluating the meand distance between the devices,
the \emph{actuators} ($\alpha$) is responsible for triggering the alarm showing a color in the screen,
and the \emph{communication} ($\chi$) component is responsible for receiving the data from the wearable devices.
